\LARGE \bf Mean Estimation from One-Bit Measurements

### 2019-12-23 preliminaries.tex
corrected various typos

A related problem is the CEO problem, which considers the estimation of a
sequence $\theta_1,\theta_2\ldots$, where a noisy version of each $\theta_i$
is available at $n$ terminals. At each terminal $i$, an encoder observes the
$k$ noisy samples
\[
X_{i,j} = \theta_j + Z_{i,j},\qquad j=1,\ldots,k, \qquad i = 1,\ldots,n,
\]
and transmits $r_i k$ bits to a central estimator~\cite{berger1996ceo}. The
central estimator produces an estimates ${\theta}_1,\ldots,{\theta}_k$ with
the goal of minimizing the quadratic risk:
\[
R_{\CEO} = \frac{1}{k} \sum_{j=1}^k \mathbb E \left[\left(\theta_j - {\theta} \right)^2 \right]. 
\]
Note that any distributed encoding scheme using one-bit per sample can be replicated $k$ times and thus leads to a legitimate encoding and estimation scheme for the CEO problem with $r_1=\ldots=r_n = 1$. It follows that, assuming that $\theta$ is drawn once from the prior $\pi$, our mean estimation problem from one-bit samples under distributed encoding corresponds to the CEO setting with $k=1$ realization of $\theta$ observed under noise at $n$ different locations, and communicated at each location using an encoder sending a single bit. 
%
Consequently, a lower bound on the MSE in estimating $\theta$ in the
distributed encoding setting is given by the minimal MSE in the CEO setting
as $k \to \infty$. Note that the difference between the CEO setting and ours
lays in the privilege of each of the encoders to describe $k$ realizations
of $\theta$ using $k$ bits with MSE averaged over these realizations, rather
than a single realization using a single bit in ours.

>>>>

A related problem is the CEO problem, which considers the estimation of a
sequence $\theta_1,\theta_2\ldots$, where a noisy version of each $\theta_j$
is available at $n$ terminals. At each terminal $i$, an encoder observes the
$k$ noisy samples
\[
X_{i,j} = \theta_j + Z_{i,j},\qquad j=1,\ldots,k, \qquad i = 1,\ldots,n,
\]
and transmits $r_i k$ bits to a central estimator~\cite{berger1996ceo}. The
central estimator produces estimates ${\hat{\theta}}_1,\ldots,{\hat{\theta}}_k$ with
the goal of minimizing the quadratic risk:
\[
R_{\CEO} = \frac{1}{k} \sum_{j=1}^k \mathbb E \left[\left(\hat{\theta}_j - {\theta_j} \right)^2 \right]. 
\]
Note that any distributed encoding scheme using one-bit per sample can be replicated $k$ times and thus leads to a legitimate encoding and estimation scheme for the CEO problem with $r_1=\ldots=r_n = 1$. It follows that, assuming that $\theta$ is drawn once from the prior $\pi$, our mean estimation problem from one-bit samples under distributed encoding corresponds to the CEO setting with $k=1$ realization of $\theta$ observed under noise at $n$ different locations, and communicated at each location using an encoder sending a single bit. 
%
Consequently, a lower bound on the MSE in estimating $\theta$ in the
distributed encoding setting is given by the minimal MSE in the CEO setting
as $k \to \infty$. Note that the difference between the CEO setting and ours
lays in the privilege of each of the encoders to describe $k$ realizations
of $\theta$ using $k$ bits with MSE averaged over these realizations, rather
than a single realization using a single bit in ours.
